Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-09-09 tex/sections/apm.tex
Fixe some typos and readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Prover Machine gets as its primary input a vector $(\mathbf{C}_H,\mathbf{C}_P,\mathbf{C}_R)$ where
$\mathbf{C}_H$ is a commitment to the AscEE Heap, $\mathbf{C}_P$ is a commitment to the AscEE program area and
$\mathbf{C}_R$ is a commitment to an ordered list of requests. The APM then outputs the updated
commitments to the AscEE heap and program area and a final $\mathbf{accept}$ flag which indicates if the execution has
ended successfully or not: $(\mathbf{C}_{H'},\mathbf{C}_{P'},\mathbf{accept})$.

@@

The APM consists of four main modules:
\begin{itemize}
    \item \textbf{Preprocessor:} This module prepares the input data for other modules. It verifies that $H,
    P,R$ are valid w.r.t the provided commitments. It also processes the input data and ensures it has the
    correct format and is valid. For example it verifies the signatures of authenticated messages or
    verifies that the proposed chunk bounds are valid.
    \item \textbf{Normal Execution Unit (NEU):} This module executes the requests whose execution completes
    normally. It outputs the updated heap chunks and an $accept_N$ flag. More formally it evaluates $(H',accept_N)=P(H,
    R_{good})$, where $H'$ is the updated heap chunks and the $accept_N$ flag will be set to false, If an
    application terminates abruptly.
    \item \textbf{Failure Repeater Unit (FRU):} This module evaluates $accept_F=P(H',R_{bad})$, where $R_{bad}$ is
    those requests whose execution terminates abnormally, $H'$ is the output of the NEU and the $accept_F$ flag is set
    to false if a request execution completes normally.

>>>>

The Argennon Prover Machine gets as its primary input a vector $(\mathbf{C}_H,\mathbf{C}_P,\mathbf{C}_R)$ where
$\mathbf{C}_H$ is a commitment to the AscEE heap, $\mathbf{C}_P$ is a commitment to the AscEE program area and
$\mathbf{C}_R$ is a commitment to an ordered list of requests. The APM then outputs the updated
commitments to the AscEE heap and program area and a final $\mathbf{accept}$ flag which indicates if the execution has
ended successfully or not: $(\mathbf{C}_{H'},\mathbf{C}_{P'},\mathbf{accept})$.

@@

The APM consists of four main modules:
\begin{itemize}
    \item \textbf{Preprocessor:} This module prepares the input data for other modules. It verifies that $H,
    P,R$ are valid w.r.t the provided commitments. It also processes the input data and ensures it has the
    correct format and is valid. For example it verifies the signatures of authenticated messages or
    checks that the proposed chunk bounds are valid.
    \item \textbf{Normal Execution Unit (NEU):} This module executes the requests whose execution completes
    normally. It outputs the updated heap chunks and an $accept_N$ flag. More formally it evaluates
    $H',accept_N=P(H,R_{good})$, where $H'$ is the updated heap chunks and $accept_N$ flag will be set to false, If an
    application terminates abruptly.
    \item \textbf{Failure Repeater Unit (FRU):} This module evaluates $accept_F=P(H',R_{bad})$, where $R_{bad}$ is
    those requests whose execution terminates abnormally, $H'$ is the output of the NEU and $accept_F$ flag is set
    to false if a request execution completes normally.

### 2022-09-09 tex/sections/avm.tex
Fixe some typos and readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Smart Contract Execution Environment (AscEE) is an abstract high level execution environment for executing
Argennon smarts contracts (a.k.a\ Argennon applications) in a secure and isolated environment. An Argennon application
essentially is an HTTP server whose state is
kept in the Argennon blockchain and its logic is described using an Argennon Standard Application Representation (ASAR).

An Argennon Standard Application Representation is a programming language for describing Argennon
applications, optimized
for the architecture and properties of the Argennon platform. This text based representation should be low level
enough to enable easy compilation from any high level programming language and should be high level enough to preserve
the high level information of the application logic and facilitate platform specific compiler optimization at a host
machine. In this regard, the ASAR can be considered as an Intermediate Representation (IR).

@@

The Argennon Smart Contract Execution Environment can be seen as a machine for executing Argennon applications to
fulfill \emph{external} HTTP requests\footnote{External requests are requests that are not made by other Argennon
applications.}, produce their HTTP responses and update related heap chunks. The execution of requests can be
considered sequential\footnote{Actually requests may be executed in parallel but by performing data dependency analysis
the result is guaranteed to be identical with the sequential execution of requests.} and each request has a separate
\emph{execution session}. Therefore, an execution session is a separate session of executing application's code in
order to fulfill an external HTTP request. We call this external request the \emph{initiator} of the execution session.

@@

During an execution session an application can make \emph{internal} HTTP requests to other applications. Those
requests will not start a new execution session and will be executed within the current session. In AscEE making an
internal HTTP request to an application is similar to a function invocation, and for that reason, we also refer to
them as \emph{application calls}.

@@

Every Argennon application has two types of memory: local memory and heap. Local memory is not persistent and is
destroyed when the application call ends. Local memory is used for storing local variables and is not directly
addressable. Heap, on the other hand, is persistent and can be used for persisting data between application calls.
Heap is addressable and provides low level direct access. Both local memory and heap are limited, but the
AscEE does not specify any particular limits for them. When an application tries to use too much memory, that may
cause the execution session to end abruptly. In that case, the execution session will not have any effects on the
state of the heap.

@@

During an execution session every heap chunk has an access type which may disallow certain operations. This access
type is declared by the initiator request of the execution session:

@@

At the start of executing requests of a block, a validator can consider two values for every
heap chunk, its size: \texttt{chunkSize} and a size upper bound: \texttt{sizeUpperBound}. The value of
\texttt{chunkSize} can be determined uniquely at the start of
every execution session, and it may be updated during the session by the owner application. On the other hand,
the value of \texttt{sizeUpperBound} is proposed by the block proposer for each block and is calculated based on values
declared by external requests (i.e.\ transactions) which want to perform chunk resizing. This value needs to be
an upper bound of all the declared resizing values and indicates the upper bound of \texttt{chunkSize} during the
execution of a block.

The value of \texttt{chunkSize}, can be modified during an execution session. However, the new values of size can
only be increasing or decreasing. More precisely, if a request declares that it wants to expand (shrink) a chunk, it
can only increase (decrease) the value of \texttt{chunkSize} and any specified value during the execution
session, needs to be greater (smaller) than the previous value of the chunk's size. Any request that wants to expand
(shrink) a chunk needs to specify a max size (min size). The value of \texttt{chunkSize} can not be set higher
(lower) than this value.

@@

Usually an application should not have any assumption about the content of memory locations that are outside the chunk.
While these locations are zero initialized at the start of every execution session, multiple
invocations of an application may occur in a single execution session, and if one of them modifies a location outside
the chunk, the changes can be seen by next invocations.

There is no way for an application to query \texttt{sizeUpperBound}. As a result, for an application
accessing offsets higher than \texttt{chunkSize} results in undefined behaviour, while the behaviour is well-defined
in the view of validators.
This enables validators to determine the validity of an offset at the start of the block validation in a parallelized
preprocessing phase without actually executing requests.

@@

The address space of a chunk starts from zero and only offsets lower than \texttt{sizeUpperBound} are valid. Trying to
access any offset higher than this value will always result in a revert for the application.

@@

All Argennon prefix trees have an equal branching factor \(\beta\)\footnote{A typical choice for \(\beta\) is \(2^8\)
    .}, and
we can represent an Argennon
prefix tree as a sequence of fractional numbers in base \(\beta\):
\[
    (A^{(1)},A^{(2)},A^{(3)},\dots)\ ,
\]
where \(A^{(i)}=(0.a_{1}a_{2}\dots a_{i})_\beta\), and we have \(A^{(i)} \leq A^{(i+1)}\). \footnote{It's possible to
have \(a_i=0\). For example, \(A^{(4)}=(0.2000)_{10}\) is correct.}

@@

The attachment of a request is a list of request identifiers of the current block that are ``attached'' to the request.
That means, for validating the request a validator first needs to ``inject'' the digest of attached requests into the
HTTP request text. By doing so, the called application will have access to the digest of attachments in a secure way.

@@

Each execution session has a list of authenticated messages. Each authenticated message has an index which will be
used for passing the message to an application as a request parameter. The AscEE uses cryptographic signatures to
authenticate messages for user accounts. The signatures are validated in parallel during the
preprocessing step, and any type of cryptographic signature scheme can be used.

@@

\section{The ArgC Language}\label{sec:the-argc-language}

\subsection{The ArgC Standard Library}\label{sec:asl}

@@

All Argennon standards, for instance ARC standard series, which defines standards regarding transferable assets,
are defined based on how a contract should use the AVM standard library. As a result, Argennon standards are
different from conventional blockchain standards. Argennon standards define some type of standard logic and
behaviour for a smart contract, not only a set of method signatures. This enables users to expect certain type
of behaviour from a contract which complies with an Argennon standard.

>>>>

The Argennon Smart Contract Execution Environment (AscEE) is an abstract high level execution environment for executing
Argennon smarts contracts (a.k.a\ Argennon applications) in an efficient and isolated environment. An Argennon
application essentially is an HTTP server whose state is
kept in the Argennon blockchain and its logic is described using an Argennon Standard Application Representation (ASAR).

An Argennon Standard Application Representation is a programming language for describing Argennon
applications, optimized
for the architecture and properties of the Argennon platform. This text based representation is low level
enough to enable easy compilation from any high level programming language and is high level enough to preserve
the high level information of the application logic and facilitate platform specific compiler optimization at a host
machine. In this regard, the ASAR can be considered as an Intermediate Representation (IR).

@@

The Argennon Smart Contract Execution Environment can be seen as a machine for executing Argennon applications to
fulfill \emph{external} HTTP requests\footnote{External requests are requests that are not made by other Argennon
applications.}, produce their HTTP responses and update related heap chunks. The execution of requests can be
considered sequential\footnote{Actually requests may be executed in parallel but by performing data dependency analysis
the result is guaranteed to be identical with the sequential execution of requests.} and each request has a separate
\emph{execution session}. In other words, an execution session is a separate session of executing application's code in
order to fulfill an external HTTP request. We call this external request the \emph{initiator} of the execution session.

@@

During an execution session an application can make \emph{internal} HTTP requests to other applications. These
requests will not start a new execution session and will be executed within the current session. In AscEE making an
internal HTTP request to an application is similar to a function invocation, and for that reason, we also refer to
them as \emph{application calls}.

@@

Every Argennon application has two types of memory: local memory and heap. Local memory is not persistent and is
destroyed when the application call ends. Local memory is used for storing local variables and is not directly
addressable. Heap, on the other hand, is persistent and can be used for persisting data between application calls.
Heap is addressable and provides low level direct access. Both local memory and heap are limited, but the
AscEE does not specify any particular limits for them. When an application tries to use too much memory, that may
cause the execution session to end abruptly. In that case, the execution session will not have any effects on the
state of heap.

@@

During an execution session every heap chunk has an access-type which may disallow certain operations. The
access-type of a chunk is declared by the initiator request of the execution session:

@@

At the start of executing requests of a block, a validator can consider two values for every
heap chunk, the size: \texttt{chunkSize} and a size upper bound: \texttt{sizeUpperBound}. The value of
\texttt{chunkSize} can be determined uniquely at the start of
every execution session, and it may be updated during the session by the owner application. On the other hand,
the value of \texttt{sizeUpperBound} is proposed by the block proposer for each block and is calculated based on values
declared by external requests (i.e.\ transactions) that want to perform chunk resizing. This value needs to be
an upper bound of all the declared resizing values and indicates the upper bound of \texttt{chunkSize} during the
execution of a block.

The address space of a chunk starts from zero and only offsets lower than \texttt{sizeUpperBound} are valid. Trying to
access any offset higher than \texttt{sizeUpperBound} will always cause the execution session to end abruptly. There
is no way for an application to query \texttt{sizeUpperBound}. As a result, in the view of an application,
accessing offsets higher than \texttt{chunkSize} will result in undefined behaviour, while the behaviour is
well-defined for validators.
This enables validators to determine the validity of an offset at the start of the block validation in a parallelized
preprocessing phase without actually executing requests.

The value of \texttt{chunkSize}, can be modified during an execution session. However, the new values of size can
only be increasing or decreasing. More precisely, if a request declares that it wants to expand (shrink) a chunk, it
can only increase (decrease) the value of \texttt{chunkSize} and any specified value during the execution
session, needs to be greater (smaller) than the previous value of the \texttt{chunkSize}. Any request that wants to
expand (shrink) a chunk needs to specify a max size (min size). The value of \texttt{chunkSize} can not be set higher
(lower) than this value.

@@

Usually an application should not have any assumptions about the content of memory locations that are outside the chunk.
While these locations are zero initialized at the start of every execution session, multiple
invocations of an application may occur in a single execution session, and if one of them modifies a location outside
the chunk, the changes can be seen by next invocations.

@@

@@

All Argennon prefix trees have an equal branching
factor \(\beta\)\footnote{A typical choice for \(\beta\) is \(2^8\).}, and we can represent an Argennon
prefix tree as a sequence of fractional numbers in base \(\beta\):
\[
    (A^{(1)},A^{(2)},A^{(3)},\dots)\ ,
\]
where \(A^{(i)}=(0.a_{1}a_{2}\dots a_{i})_\beta\), and we have \(A^{(i)} \leq A^{(i+1)}\). \footnote{It's possible to
have \(a_i=0\). For example, \(A^{(4)}=(0.2000)_{10}\) is correct.}

@@

The attachment of a request is a list of request identifiers of the current block that are \emph{attached} to the
request. That means, for validating the request a validator first needs to \emph{inject} the digest of attachments
into the current HTTP request text. By doing so, the called application will have access to the digest of
attachments in a secure and authenticated way.

@@

Each execution session has a list of authenticated messages. Each authenticated message has an index which will be
used for passing the message to an application as a request parameter. The AscEE uses cryptographic signatures to
authenticate messages for user accounts. The signatures are validated during the
preprocessing step in parallel, and any type of cryptographic signature scheme can be used.

@@

\section{The ArgC Language}\label{sec:the-argc-language}
\note{This section is outdated...}
\subsection{The ArgC Standard Library}\label{sec:asl}

@@

All Argennon standards, for instance ARC standard series, which defines standards regarding transferable assets,
are defined based on how a contract should use the ArgC standard library. As a result, Argennon standards are
different from conventional blockchain standards. Argennon standards define some type of standard logic and
behaviour for a smart contract, not only a set of method signatures. This enables users to expect certain type
of behaviour from a contract which complies with an Argennon standard.

### 2022-09-09 tex/sections/blocks.tex
Fixe some typos and readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

To validate a block three main conditions need to be verified: (i) commitments to the program and heap
database result from applying the request list and clustering directives of the block to the previous AscEE
state, (ii) $v \mhyphen cert_{h-k}$ is valid, (iii) previous block is valid and has height $h - 1$.

@@

The certificate of validators, $v \mhyphen cert_{h-k}$, is an aggregate signature; validating it requires accessing the
AscEE heap state at block $h-k-1$ to obtain public keys and stake values. Again, in addition to direct verification,
a validator can use computation proofs, received from the Argennon cloud, to perform cheaper verification.

For validating the previous block, instead of directly validating the content of the block, a validator only
verifies the block certificates. Verifying $d \mhyphen cert_{h-1}$ is straightforward and verifying $v \mhyphen
cert_{h-1}$ can be cheaply done by using computation proofs, obtained from the Argennon cloud. This type of block
validation only validates the transition from block $h-1$ to block $h$, and the block is valid only if its previous
block is valid too. We
call this type of block verification \emph{conditional} block validation, since the validity of the current block is
conditioned on the validity of the previous block.

>>>>

To validate a block three main conditions need to be validated: (i) commitments to the program and heap
database result from applying the request list and clustering directives of the block to the previous AscEE
state, (ii) $v \mhyphen cert_{h-k}$ is valid, (iii) previous block is valid and has height $h - 1$.

@@

The certificate of validators, $v \mhyphen cert_{h-k}$, is an aggregate signature. Validating it requires accessing the
AscEE heap state at block $h-k-m$ to obtain public keys and stake values. Here $m$ is the total number of validator
assemblies and $k$ is the maximum allowed length of
the unvalidated chain. (See Section\ref{subsec:validators-committee})
Again, in addition to direct verification, a validator can use computation proofs, received from the Argennon cloud,
to perform cheaper verification of this certificate.

For validating the previous block, instead of directly validating the content of the block, a validator only
verifies the block certificates. Verifying $d \mhyphen cert_{h-1}$ is straightforward. Verifying $v \mhyphen
cert_{h-1}$, which should be performed based on stakes at block $h-m-1$, can be cheaply done by using computation
proofs, obtained from
the
Argennon cloud.

This type of block validation only validates the transition from block $h-1$ to block $h$, and the block is valid
only if its previous block is valid. We
call this type of block validation \emph{conditional block validation}, since the validity of the current block is
conditioned on the validity of the previous block.

### 2022-09-09 tex/sections/consensus.tex
Fixe some typos and readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon protocol calculates a stake value for every account, which is an estimate of a user's stake in the
system, and is measured in ARGs. Any account whose stake value is higher than
\texttt{minValidatorsStake} threshold is considered a \emph{validator}.
The \texttt{minValidatorsStake}
threshold is determined by the ADAGs, but it can never be higher than $500$ ARGs.

Every \texttt{committeeLifeTime} number of blocks, randomly $m$ committees are selected from
validators, in a way that the total stakes of committees are almost equal, and every
account is a member of \textbf{at least} one committee.

@@

\note{When a validator changes his status, the change has no effect until the block containing the status
change transaction gets certified by his committee.}

A block certificate issued by some members of a validators assembly is considered valid, if according to
the staking database of the previous block \textbf{certified by the same committee}, we have:\footnote{If we calculate
the stake values based on the previous block a malicious committee can select the validators of the next block.}
\begin{itemize}
    \item The total stake of \texttt{online} members of the committee is higher than \texttt{minOnlineStake} fraction
    of the total stake of the committee. This threshold can be changed by the ADAGs, but it can never be lower
    than $2/3$.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than $3/4$ of the total stake
    of the committee members that have \texttt{online} status.
\end{itemize}

The delegates can generate blocks very fast. Therefore, the Argennon blockchain always has an
unvalidated part, which contains blocks that have a certificate from the committee of delegates but have not
yet received a certificate from the validators.

As we mentioned before, the block with height $n$ needs a certificate from the assembly of
validators with index $n$ modulo $m$. To decide about signing the certificate of a block which already has
a certificate from the delegates, a validator checks the conditional
validity\footnote{See Section~\ref{subsec:block-validation}} of the block, and
if the block is valid he issues
an "accept" signature. If the block is invalid, he initiates the recovery protocol. The validator will broadcast the
certificate \textbf{only after} he sees the certificate of the validators of the previous block.
Some validators may also require seeing a certificate from
some community driven committee. An honest validator never signs a certificate for two different blocks with the
same height.

So in Argennon, the block validation by committees is performed in parallel, and validators
do not wait for seeing the certificate of the previous block validators to start transaction validation. On the
other hand, the block certificates are published and broadcast sequentially. A validator does not publish its
certificate if the certificate of the previous block has not been published yet. This ensures that an invalid
fork made by malicious delegates will not receive any certificates from validators.

>>>>

The Argennon protocol calculates a stake value for every account, which is an estimate of a user's stake in the
system, and is measured in ARGs. Any account whose stake value is higher than
\texttt{minValidatorsStake} threshold is considered a \emph{validator}.
The \texttt{minValidatorsStake}
threshold is determined by the ADAGs, but it can never be higher than $1000$ ARGs.

Every \texttt{AssemblyLifeTime} number of blocks, randomly $m$ assemblies are selected from
validators, in a way that the total stakes of assemblies are almost equal, and every
account is a member of \textbf{at least} one assembly.

@@

\note{When a validator changes his status, the change has no effect until the block containing the status
change transaction gets certified by his assembly.}

A block certificate issued by some members of a validators assembly is considered valid, if according to
the staking database of the previous block \textbf{certified by the same assembly}, we have:\footnote{If we calculate
the stake values based on the previous block a malicious assembly can select the validators of the next block.}
\begin{itemize}
    \item The total stake of \texttt{online} members of the assembly is higher than \texttt{minOnlineStake} fraction
    of the total stake of the assembly. This threshold can be changed by the ADAGs, but it can never be lower
    than $2/3$.
    \item All signers of the certificate have \texttt{online} status.
    \item The sum of stake values of the certificate signers is higher than $3/4$ of the total stake
    of the assembly members that have \texttt{online} status.
\end{itemize}

The delegates can generate blocks very fast. Therefore, the Argennon blockchain always has an
unvalidated part, which contains blocks that have a certificate from the assembly of delegates but have not
yet received a certificate from the validators.

As we mentioned before, the block with height $n$ needs a certificate from the assembly of
validators with index $n$ modulo $m$. To decide about signing the certificate of a block which already has
a certificate from the delegates, a validator checks the conditional
validity\footnote{See Section~\ref{subsec:block-validation}} of the block, and
if the block is valid he issues
an "accept" signature. If the block is invalid, he initiates the recovery protocol. The validator will broadcast the
certificate \textbf{only after} he sees the certificate of the validators of the previous block.
Some validators may also require seeing a certificate from
some community driven committees. An honest validator never signs a certificate for two different blocks with the
same height.

So in Argennon, the block validation by assemblies is performed in parallel, and validators
do not wait for seeing the certificate of the previous block assembly to start block validation. On the
other hand, the block certificates are published and broadcast sequentially. A validator does not publish its
certificate if the certificate of the previous block validator assembly has not been published yet. This ensures that
an invalid fork made by malicious delegates will not receive any certificates from any validator assemblies.

### 2022-09-09 tex/sections/elements.tex
Remove the update notice
We remove the update notice, but the chapter is not finished yet.

Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Fixe some typos and readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

An application identifier, \texttt{applicationID}, is
a unique prefix code generated by the \emph{applications} prefix tree. (See Section~\ref{sec:identifiers}.)
An application identifier can be considered as the address of an application and has the following standard symbolic
representation:
\begin{verbatim}
<application-id> ::= <decimal-prefix-code>
<decimal-prefix-code> ::= <dec-num>"."<decimal-prefix-code> | <dec-num>
\end{verbatim}
where \texttt{<dec-num>} is a normal decimal number between $0$ and $255$. For example \texttt{21.255.37},
\texttt{0}, \texttt{11.6} and \texttt{2.0.0.0.0}, are valid application addresses.

@@

Argennon application use HTTP as the application protocol and they are advised to have a RESTful API design.

@@

The ARG application or the ARG smart contract,
with \texttt{applicationID = 1}, controls the ARG token, the main
currency of the Argennon blockchain. This smart contract also manages a database of public keys and
handles signature verification.

@@

A new account can be created by sending a proper HTTP request to the ARG smart contract. For creating
a new account two public keys need to be provided by the caller and registered in the Argennon smart contract.
One public key will be used for issuing digital signatures, and the other one will be used for voting. The
provided public keys need to meet certain cryptographic requirements,\footnote{Argennon uses Prove
Knowledge of the Secret Key (KOSK) scheme.} and can not be already registered in the system.

@@

\subsection{Resource Declaration}\label{subsec:resource-declaration}

@@

\begin{itemize}
    \item Maximum AscEE clocks
    \item The list of applications the request will call
    \item The list of access blocks the request needs
    \item \texttt{maxSize} for chunks it wants to expand
    \item \texttt{minSize} for chunks it wants to shrink
    \item A list of applications it will update (if any)
\end{itemize}

@@

caps:
    maxClocks: 150 # maximum number of AVM execution clocks
    apps: [1,124.16]
    read: [(2654,3),(15642,0),(15642,1),(15642,3)]
    write: [(15642,0),(20154,0),(20154,1)]
\end{lstlisting}

@@

If a proposed block contains many transactions which need a lot of run-time resources, validators would not
be able to validate all transactions in a timely manner. Consequently, they may decide to reject the block or if they
spend enough resources, the confirmation of that block could take more than usual. Longer block time is not
favoured by block proposers, because it means less throughput of the system which usually means less overall rewards
for them. In the Argennon protocol the management of run-time resources, is left to the block proposer.

In Argennon the reference for resource usage is the Argennon Prover Machine. The APM has two different execution
units: the NEU which is used for executing external requests that the block proposer claims will complete
successfully and the FRU which executes requests that the proposer has classified as failed requests. The FRU has a
more restricted resource management and less resources are available for requests that use the FRU.

We recall from Section~\ref{ch:APM} that the APM configuration is a tuple:
\[
(\mathcal{S},\mathcal{L}_{\text{NEU}},\mathcal{L}_{\text{FRU}},\mathcal{T}_{\text{NEU}},\mathcal{T}_{\text{FRU}}).
\]
When requests are executed by the APM, the following run-time resources should be considered:

@@

    For executing all request of a block, at max, The NEU will run for
    $\mathcal{T}_{\text{NEU}}$ steps and the FRU will run for
    $\mathcal{T}_{\text{FRU}}$ steps.

    \item \textbf{local memory}: $\mathcal{L}_{\text{NEU}}, \mathcal{L}_{\text{FRU}}$. The Argennon protocol requires
    $\mathcal{L}_{\text{NEU}} = 3\mathcal{L}_{\text{FRU}}$, so the NEU has three times more local memory.

@@

In Argennon the proposer does not use the APM for executing requests and directly executes the ASAR of an
application, which is much more efficient. Only when he wants to reject a transaction because of excessive resource
usage, he will emulate the APM to make sure that the request will be rejected by the FRU. The differences between the
NEU and FRU ensures that this policy is safe.

>>>>

An application identifier, \texttt{applicationID}, is a unique prefix code generated by the \emph{applications}
prefix tree. (See Section~\ref{sec:identifiers}) An application identifier can be considered as the address of an
application and has the following standard symbolic representation:
\begin{verbatim}
<application-id> ::= <decimal-prefix-code>
<decimal-prefix-code> ::= <dec-num>"."<decimal-prefix-code> | <dec-num>
\end{verbatim}
where \texttt{<dec-num>} is a normal decimal number between $0$ and $255$.

For example \texttt{21.255.37}, \texttt{0}, \texttt{11.6} and \texttt{2.0.0.0.0}, are valid symbolic
representations of application addresses.

@@

Argennon applications use HTTP as the application protocol, and they are advised to have a RESTful API design.

@@

The ARG application or the ARG smart contract,
with \texttt{applicationID = 1}, controls the ARG token, the main
currency of the Argennon blockchain. This smart contract also manages a database of public keys and stake values.

@@

A new account can be created by sending a proper HTTP request to the ARG smart contract. For creating
a new account two public keys need to be provided by the caller and registered in the Argennon smart contract.
One public key will be used for issuing digital signatures, and the other one will be used for voting. The
provided public keys need to meet certain cryptographic requirements.\footnote{Argennon uses Prove
Knowledge of the Secret Key (KOSK) scheme.}

@@

\subsection{Resource Declaration Object}\label{subsec:resource-declaration}

@@

\begin{itemize}
    \item Maximum execution cost
    \item The list of applications the request will call
    \item The list of chunks the request needs
    \item \texttt{maxSize} for chunks it wants to expand
    \item \texttt{minSize} for chunks it wants to shrink
    \item A list of applications it will update (if any)
\end{itemize}

@@

caps:
    maxCost: 150      # the cost of execution by the APM
    apps: [1,124.16]
    read: [(2654,3),(15642,0),(15642,1),(15642,3)]
    write: [(15642,0),(20154,0),(20154,1)]
\end{lstlisting}

@@

If a proposed block contains many transactions which need a lot of run-time resources, validators would not
be able to validate all transactions in a timely manner. Consequently, they may decide to reject the block or if they
spend enough resources, the confirmation of that block could take more than usual. Longer block time is not
favoured by block proposers, because it means less throughput of the system which usually means less overall rewards
for them.

In the Argennon protocol the management of run-time resources, is left to the block proposer.
In Argennon the reference for resource usage is the Argennon Prover Machine. The APM has two different execution
units: the NEU which is used for executing external requests that the block proposer claims will complete
successfully and the FRU which executes requests that the proposer has classified as failed requests. The FRU has a
more restricted resource management and less resources are available for requests that use the FRU\@.

We recall from Chapter~\ref{ch:APM} that the APM configuration is a tuple:
\[
(\mathcal{S},\mathcal{L}_{\text{NEU}},\mathcal{L}_{\text{FRU}},\mathcal{T}_{\text{NEU}},\mathcal{T}_{\text{FRU}}).
\]
When requests are executed by the APM, the following run-time resources should be considered:

@@

    For executing the whole requests of a block, at max, The NEU will run for
    $\mathcal{T}_{\text{NEU}}$ steps and the FRU will run for
    $\mathcal{T}_{\text{FRU}}$ steps.

    \item \textbf{local memory}: denoted by $\mathcal{L}_{\text{NEU}}, \mathcal{L}_{\text{FRU}}$. The Argennon protocol
    requires: $\mathcal{L}_{\text{NEU}} = 3\mathcal{L}_{\text{FRU}}$, so the Normal Execution Unit has three
    times more local memory.

@@

In Argennon the proposer does not use the APM for executing requests and directly executes the ASAR of an
application. That is much more efficient. Only when the proposer wants to reject a transaction due to excessive
resource usage, he will emulate the APM to make sure the request will be rejected by the FRU. The differences
between the NEU and FRU ensures that this policy is safe.

### 2022-09-09 tex/sections/persistence.tex
Fixe some typos and readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

In the AscEE persistence layer, similar objects are clustered together and constitute a bigger data element which we
call a \emph{page}.\footnote{we avoid calling them clusters, because usually a cluster refers to a \emph{set}. AscEE
chunk clusters are not sets. They are ordered lists, like a page containing an ordered list of words or sentences.}
A page is an ordered list of an arbitrary number of chunks. Every page has a \emph{native} chunk that has the same
identifier as the page. In addition to the native chunk, a page can host any number of \emph{migrant} chunks.
A page of the AscEE storage should consists of chunks that have very similar access patterns. Ideally, when a page is
needed for validating a block, almost all of its chunks should be needed for either reading or writing. We prefer
that the chunks are needed for the same access type. In other words, the chunks of a page should be chosen in a way that
for validating a block, we need to either read all of them or modify\footnote{and probably read.} all of them.

@@

Pages of the AscEE storage are persisted using \emph{dynamic universal accumulators}. Argennon
has two dynamic accumulators: \emph{program} database, which stores the AscEE program area, and \emph{heap} database,
which stores the AscEE heap. The commitment of these accumulators are included in every block of the Argennon
blockchain. In the Argennon cloud, nodes that store these accumulators are called Publicly Verifiable Database
(PV-DB) servers.

@@

The commitments of the AscEE cryptographic accumulators are affected by the way data chunks are clustered in pages.
Therefore, the Argennon clustering algorithm has to be a part of the consensus protocol.

@@

A block proposer is allowed to obtain clustering directives from any third party source\footnote{we can say the AscEE
clustering algorithm is essentially off-chain.}. This will not
affect Argennon security, since the integrity of a database can not be altered by clustering directives.
Those directives can only affect the performance of the Argennon network, and directives of a single block can
not affect the performance considerably.

>>>>

In the AscEE persistence layer, similar objects are clustered together and constitute a bigger data element which we
call a \emph{page}.\footnote{We avoid calling them clusters, because usually a cluster refers to a \emph{set}. AscEE
chunk clusters are not sets. They are ordered lists, like a page containing an ordered list of words or sentences.}
A page is an ordered list of an arbitrary number of chunks. Every page has a \emph{native} chunk that has the same
identifier as the page. In addition to the native chunk, a page can host any number of \emph{migrant} chunks.
A page of the AscEE storage should consist of chunks that have very similar access patterns. Ideally, when a page is
needed for validating a block, almost all of its chunks should be needed for either reading or writing. We prefer
that the chunks are needed for the same access type. In other words, the chunks of a page should be chosen in a way that
for validating a block, we need to either read all of them or modify\footnote{and probably read.} all of them.

@@

Pages of the AscEE storage are persisted using \emph{dynamic universal accumulators}. Argennon
has two dynamic accumulators: \emph{program} database, which stores the AscEE program area, and \emph{heap} database,
which stores the AscEE heap. The commitment of these accumulators are included in every block of the Argennon
blockchain. In the Argennon cloud, nodes that store these accumulators are called Publicly Verifiable Database
(PV-DB) servers.\footnote{Usually PVC servers are also PV-DB servers.}

@@

The commitments of the AscEE cryptographic accumulators are affected by the way chunks are clustered in pages.
Therefore, the Argennon clustering algorithm has to be a part of the consensus protocol.

@@

A block proposer is allowed to obtain clustering directives from any third party source.\footnote{We can say the AscEE
clustering algorithm is essentially off-chain.} This will not
affect Argennon security, since the integrity of a database can not be altered by clustering directives.
Those directives can only affect the performance of the Argennon network, and directives of a single block can
not affect the performance considerably.
